---
title: "Cuckoo ARU Pilot Data Exploration"
author: "Anna Kurtin"
date: "2022-09-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(data.table)
```

Add in the code for analyzing the preliminary data here

```{r}
# Load in data


locations <- read_csv("C:\\Users\\annak\\OneDrive\\Documents\\UM\\Research\\Thesis_ArcGIS_Files\\Cuckoo_Monitoring_Locations\\AudioMoth_Deployment_Location_Data.csv")

# Need to change 97_3 to make the 109 coordinate negative to put it on the right hemisphere



# What does the score range between?
min(bbcu$score)
max(bbcu$score)
# says 14.55 even though the max score given to any file in the field dataset is 10.97
# review the continuous score occupancy models and the data summary file for this

summary(bbcu)



```


# Organizing classifier results from 2020

This is data from 2020 that was run through the automatic classifier

* This is still around the upper limit of cells in a csv opened in excel (1048576) - email Andy to make sure you're not missing nay of the data

```{r}
# Load in data *DO NOT OPEN IN EXCEL*
classifier_20 <- read_csv("C:\\Users\\annak\\OneDrive\\Documents\\UM\\Research\\UM Masters Thesis R Work\\Data\\Classifier Results\\annotations_standardmodel_BBCU_classifier_results_2020.csv")
# See if the other data is different
c_20 <- read_csv("C:\\Users\\annak\\OneDrive\\Documents\\UM\\Research\\UM Masters Thesis R Work\\Data\\annotations_standardmodel_epoch499_clean.csv")
c_20 <- read_csv("C:\\Users\\annak\\OneDrive\\Documents\\UM\\Research\\UM Masters Thesis R Work\\Data\\annotations_standardmodel_epoch499.csv")


# Try as data table
c_20DT <- setDT(classifier_20)

# load in data *DO NOT OPEN IN EXCEL*
classifier_21 <- read_csv("C:\\Users\\annak\\OneDrive\\Documents\\UM\\Research\\UM Masters Thesis R Work\\Data\\Classifier Results\\andy_bbcu_scores_21-11-24_classifier_results_2021.csv")

# Work with as data table
c_21DT <- setDT(classifier_21)

classifier_20 <- fread("C:\\Users\\annak\\OneDrive\\Documents\\UM\\Research\\UM Masters Thesis R Work\\Data\\Classifier Results\\annotations_standardmodel_BBCU_classifier_results_2020.csv")
classifier_21 <- fread("C:\\Users\\annak\\OneDrive\\Documents\\UM\\Research\\UM Masters Thesis R Work\\Data\\Classifier Results\\2021_BBCU_Classifier_Results.csv")
```

Renaming 2020 and 2021 classifier data:
**Before you do this make sure you're clear on which site name line up with which point ID

- Split up the "tag" column in the classifier to isolate the AudioMoth ID (Call it Moth_ID)
- Load in the metadata file that has all of the point ID names and the Moth ID columns
- Left join? them based on the Moth ID and the start of the tag column
- join back the Point ID to the name of the data file

```{r}
# Load in metadata
metdat_20 <- read_csv("C:/Users/annak/OneDrive/Documents/UM/Research/UM Masters Thesis R Work/Data/2020_ARUDeploymentMetadata_ARUandPlaybackResults.csv")

# Split the file column into two columns, one for ID and one for timedatte
c_20DT[,c("Moth_ID","timedate") :=tstrsplit(tag,"/",fixed=TRUE)]

# join the metadata with the classifier data
#_________________________________________________

```


Getting deliverables from 2021 classifier data:
- Split off the first part of the name to ID the site/card
- Split off the date and time into separate columns
- Decide a cutoff point (based on progress report) to determine a positive presence of a cuckoo
- Use this cutoff point to add a new column of probability of cuckoo presence (high/med/low or just a yes/no?)
- Add this data to a map to send to collaborators
- Interactive map where if you click on the point it'll tell you when a cuckoo was detected and a histogram of the dates it was detected

```{r 2021 Classifier Wrangling}

# Separate the first column into ID and timestamp columns
# system.time({
#   classifier_21%>% separate(file, into = c("ID", "timestamp"), sep = "/") %>% separate(timestamp, into = c("date","time"), sep="_") %>% separate(time, into = c("time","file_type"), sep = ".")
# })
## Way slower, do not use

# Using a data table

# Split the file column into two columns, one for ID and one for timedatte
c_21DT[,c("SD_card","timedate") :=tstrsplit(file,"/",fixed=TRUE)]
## What does fixed=TRUE do? Ask Jordan
# Split the timedate column into two columns, one for date and one for time/WAV 
c_21DT[,c("date","time") :=tstrsplit(timedate,"_",fixed=TRUE)]
# Split the time column into two columns, one for time and one for wav file type
c_21DT[,c("time","file_type") :=tstrsplit(time,".",fixed=TRUE)]
# Remove the unnecessary columns of timedate
c_21DT[,timedate :=NULL]

## create another column for yes/no if cuckoos were detected (set a reasonable cutoff point on the classifier score)

# Add in a site ID variable - Join the site ID data by SD card number 
## read in AudioMoth Deployment Metadata csv
### create a year column by splitting up the date retrieved column
### filter by just 2021 data 
## join to the classifier data from 2021
## create a map of the data to send to collaborators 

```

